Visualizing predictions

### 2021-02-08 effects_writeup.Rnw
Updated glossary
Comparing base R with varpred and emmeans

\title{Marginal predictions}

@@

<<set_up, echo=FALSE>>=
library(ggplot2)
library(margins)
library(effects)
library(emmeans)
library(jdeffects)
jdtheme()
@

@@

## varpred
simple_vpred_spec <- condsummary(mod_list=simple_models, fun=function(x, f){
		dd <- varpred(x, f)
	}, simplify = TRUE, combine = "rbind"
	, scale_param = scale_param, fmethod = "varpred"
)

@@

\begin{figure}
\begin{center}
<<vapred_isolate_numeric, fig=TRUE>>=
## Centered predictions from unscaled model
vpred_c <- varpred(lm_u, focal = "x1u", isolate = TRUE)
plot(vpred_c)
@
\caption{Using \pkg{varpred} to obtain marginal predictions from unscaled model.}
\label{fig:varpred_isolate_num}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
<<simple_margpred_cat_plot, fig=TRUE, echo=FALSE>>=
simple_margpred_cat_plot
@
\end{center}
\caption{Conditional predictions.}
\end{figure}

>>>>

\title{Visualizing predictions}

@@

<<set_up, echo=FALSE>>=
library(ggplot2)
library(margins)
library(effects)
library(emmeans)
library(jdeffects); jdtheme()

#library(shellpipes)
#sourceFiles()

@

@@

## varpred
simple_vpred_spec <- condsummary(mod_list=simple_models, fun=function(x, f){
		dd <- varpred(x, f, steps=101)
	}, simplify = TRUE, combine = "rbind"
	, scale_param = scale_param, fmethod = "varpred"
)

@@

\begin{figure}[H]
\begin{center}
<<vapred_isolate_numeric, fig=TRUE>>=
## Centered predictions from unscaled model
vpred_c <- varpred(lm_u, focal = "x1u", isolate = TRUE)
plot(vpred_c)
@
\caption{Using \pkg{varpred} to obtain marginal predictions from unscaled model.}
\label{fig:varpred_isolate_num}
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
<<simple_margpred_cat_plot, fig=TRUE, echo=FALSE>>=
simple_margpred_cat_plot
@
\end{center}
\caption{Conditional predictions.}
\end{figure}

\subsubsection{Comparison with base R predict}

<<compare_baseR, echo=FALSE>>=
load("predict_plots.rda")
@

Compare prediction estimates from \pkg{base R}, \pkg{emmeans} and \pkg{varpred}

<<>>=
## Base R vs emmeans
all.equal(base, emm)
## Base R vs varpred
all.equal(base, jd)
## Implied: emmeans vs varpred
@

\begin{figure}[H]
\begin{center}
<<compare_baseR_plot, fig=TRUE, echo=FALSE>>=
print(x1_plot)
@
\end{center}
\caption{Conditional predictions.}
\end{figure}
